% Welcome! This is the unofficial University of Udine beamer template.

% See README.md for more informations about this template.

% This style has been developed following the "Manuale di Stile"
% (Style Manual) of the University of Udine. You can find the
% manual here: https://www.uniud.it/it/ateneo-uniud/ateneo-uniud/identita-visiva/manuali-immagine-stile/manuale-stile

% Note: for some reason, the RGB values specified in the manual
% do NOT render correctly in Beamer, so they have been redefined
% for this document using the high level chromo-optic deep neural 
% quantistic technology offered by Microsoft Paint's color picker.

% We defined four theme colors: UniBrown, UniBlue, UniGold
% and UniOrange. For example, to write some uniud-brownish
% text, just use: \textcolor{UniBrown}{Hello!}

% Note that [usenames,dvipsnames] is MANDATORY due to compatibility
% issues between tikz and xcolor packages.

\documentclass[usenames,dvipsnames]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usetheme{uniud}

%%% Bibliography
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{bibliography.bib}

%%% Suppress biblatex annoying warning
\usepackage{silence}
\WarningFilter{biblatex}{Patching footnotes failed}

%%% Some useful commands
% pdf-friendly newline in links
\newcommand{\pdfnewline}{\texorpdfstring{\newline}{ }} 
% Fill the vertical space in a slide (to put text at the bottom)
\newcommand{\framefill}{\vskip0pt plus 1filll}


\title[University of Udine Unofficial Beamer Theme]{On The Explosion of Large Death Stars}
\date[May 1977]{May 25, 1977}
\author[Luke Skywalker]{
  Luke Skywalker, Ph.D.
  \pdfnewline
  \texttt{luke.skywalker@uniud.it}
}
\institute{Department of Physics, University of Udine}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Outline}
\tableofcontents
\end{frame}

\section{Before you start}
\begin{frame}{Overleaf users}

\begin{alertblock}{Warning}
You can ignore this slide if you're \textbf{not} working with Overleaf.
\end{alertblock}

\vskip 0.5cm

Overleaf, Beamer and Biber do not always get along well together. For this reason, if you make a mistake while writing this presentation, in the drop-down error message you'll \textbf{always} get Biber-related error messages.

\vskip 0.5cm

Luckily, you just have to click on ``\texttt{go to first error/warning}'' and the UI will scroll to the line containing your mistake.

\end{frame}

\begin{frame}[fragile]
\frametitle{Compiling}

\begin{alertblock}{Warning}
You can ignore this slide if you're working with Overleaf.
\end{alertblock}

To compile this deck you'll need the \texttt{biber} package. Probably your \TeX editor already supports it; if not, you will easily find online the instructions to install it.

\vskip 0.5cm

If you're not using an editor, you can compile this presentation using the command line by running:

\begin{verbatim}
$ pdflatex main.tex
$ biber main.bcf
$ pdflatex main.tex
$ pdflatex main.tex
\end{verbatim}


\end{frame}

\section{Colors}

\begin{frame}{Colors}

For this template we defined four colors, following the Style Manual of the University of Udine:
\begin{itemize}
\item \textcolor{white}{\marker{\texttt{UniOrange}}}
\item \textcolor{white}{\marker[UniBlue]{\texttt{UniBlue}}}
\item \textcolor{white}{\marker[UniBrown]{\texttt{UniBrown}}}
\item \textcolor{white}{\marker[UniGold]{\texttt{UniGold}}}
\end{itemize}

\vskip 0.5cm

You can use these colors as you want in your presentation. For example, you can \textbf{\textcolor{UniGold}{color the text in gold}} by writing \texttt{\textbackslash\{UniGold\}\{my gold text\}}.

\vskip 0.5cm

We also redefined many of the most common \LaTeX{} and Beamer commands, like \texttt{itemize}, \texttt{block}, etc. You will see samples of these commands in the following slides.

\end{frame}

\section{Blocks}

\begin{frame} 
\frametitle{This is a page with a title and a subtitle} 
\framesubtitle{And also some blocks.} 
\begin{block}{Goal of the mission}
Shoot in the Death Star's exhaust port and destroy it before the it can fire on the Rebel base.
\end{block} 
\begin{alertblock}{Take care!}
TIE Fighters may chase you while approaching the target.
\end{alertblock} 
\begin{exampleblock}{Use the force you must}
Remember your training with Obi-Wan, and use the Force to make the perfect shoot.
\end{exampleblock} 

\end{frame}

\section{Enumerates, itemizes and description}

\subsection{Enumerates and itemizes}

\begin{frame}{Enumerates and itemizes}

This is an example of \texttt{itemize}.
\begin{itemize}
	\item A long time ago in a galaxy far, far away...
\end{itemize}
And this is an example of \texttt{enumerate}.

\begin{enumerate} 
  \item Go to the Death Star.
  \item Find the exhaust port.
  \item Make the perfect shot.
  \item Become an hero.
\end{enumerate}
\end{frame}

\subsection{Description}

\begin{frame}[fragile]
\frametitle{Description}
This is an example of \texttt{description}.

\begin{description}
\item<2->[Vader] \emph{I am} your father.
\item<1->[Luke] No. No! That's not true! \textbf{That's impossible!}
\end{description}

\begin{uncoverenv}<3>
  \vskip 0.5cm
  And while we're here, let's have a look to \texttt{verbatim} as well, to see how we made items appear in arbitrary order:
  \vskip 0.5cm
  \begin{verbatim}
\begin{description}
  \item<2->[This is the first item] one
  \item<1->[This is the second item] two
\end{description}
  \end{verbatim}
\end{uncoverenv}

\end{frame}

\section{Maths}

\begin{frame}{Maths}
A formula will look like this: 
\begin{center}
 $x^2 + y^2 = z^2$
\end{center}

You can number equations as well:
\begin{equation}
1+1=2
\end{equation}

\begin{equation}
1+1=2 \tag{custom label!}
\end{equation}

\vskip 0.5cm

If you want to use the default \LaTeX{} math fonts, just go to \texttt{beamerfontthemeuniud.sty} and uncomment the line containing `\texttt{\textbackslash usefonttheme[onlymath]\{serif\}}'.

\end{frame}

\begin{frame}{Theorems}

The usual \texttt{theorem}, \texttt{corollary}, \texttt{definition}, \texttt{definitions}, \texttt{fact}, \texttt{example} and \texttt{examples} blocks are available as well.

\begin{theorem}
There exists an infinite set.
\end{theorem}
\begin{proof}
This follows from the axiom of infinity.
\end{proof}
\begin{example}[Natural Numbers]
The set of natural numbers is infinite.
\end{example}

\end{frame}

\section{Other blocks}

\begin{frame}{Other blocks}

Here we display examples of \texttt{abstract}, \texttt{verse}, \texttt{quotation}, and \texttt{quote}.

\vskip 0.5cm

\begin{abstract}
This is an abstract.
\end{abstract}
\begin{verse}
This is a verse.
\end{verse}
\begin{quotation}
This is a quotation.

\raggedleft -Han Solo
\end{quotation}
\begin{quote}
A quote this is.

\raggedleft -Yoda
\end{quote}

\end{frame}

\section{Bibliography and Publications}
\begin{frame}[fragile]
\frametitle{Bibliography}

You can cite an article
\begin{itemize}
\item normally using \texttt{\textbackslash cite}, e.g.: (\cite{article1})
\item or display the full citation using \texttt{\textbackslash fullcite}, e.g.:  \fullcite{article1}
\end{itemize}

\vskip 0.5cm
Look at the code of the following slide to see how to automatically split the bibliography on many slides. You can also use \texttt{\textbackslash nocite\{*\}} to display the non-cited publications as well.

\end{frame}

\begin{frame}[t,allowframebreaks]
\frametitle{Bibliography}

\nocite{*} % will display the non-cited publications as well. Useful for a publication list.

\printbibliography

\end{frame}

\section{Bonus Commands}

\begin{frame}[fragile]
\frametitle{Framecard}

You can display a frame with a colored background and a huge text in the center using the command \texttt{\textbackslash framecard}.
\vskip 0.5cm 
For example, you can write:
\begin{verbatim}
\framecard{A SECTION\\TITLE}
\end{verbatim}

This will display a frame with a orange background and the phrase "A SECTION TITTLE" in the center. You can also use a custom color with \texttt{\textbackslash framecard}:
\begin{verbatim}
\framecard{A SECTION\\TITLE}
\framecard[UniBlue]{A SECTION TITLE\\
WITH A CUSTOM COLOR}
\end{verbatim}
You can see the results of the commands above in the following slides.

\end{frame}

\framecard{A SECTION\\TITLE}
\framecard[UniBlue]{A SECTION TITLE\\WITH A CUSTOM COLOR}

\begin{frame}[fragile]
\frametitle{Framepic}

You can display a frame with a background image using the command \texttt{\textbackslash framepic}. The image will be \textbf{adapted vertically} to fit the the frame. 

For example, you can write:
\begin{verbatim}
\framepic{graphics/darth}{
	\framefill
    \textcolor{white}{Luke,\\I am your supervisor}
    \vskip 0.5cm
}
\end{verbatim}

Alternatively, to make the background 50\% transparent, you can write \texttt{\textbackslash framepic[0.5]\{graphics/darth\}...}


You can see the results of the commands above in the following slides.

\end{frame}


\framepic{graphics/darth}{
	\framefill
    \textcolor{white}{Luke,\\I am your supervisor}
    \vskip 0.5cm
}

\framepic[0.5]{graphics/darth}{
	\vfill
    \begin{flushright}
    \textcolor{red}{\textbf{Right-aligned text with\\Semi-transparent background}}
    \end{flushright}	
}

\begin{frame}[t,fragile,allowframebreaks]
\frametitle{Other bonus commands}

We provide two other bonus commands:
\begin{description}
\item[\texttt{pdfnewline}] you can use \texttt{\textbackslash pdfnewline} to avoid the annoying \texttt{hyperref} related warnings when using newlines in the document's title, author, etc. For example, in this presentation the author is defined as:
\begin{verbatim}
\author[Luke Skywalker]{
  Luke Skywalker, Ph.D.
  \pdfnewline
  \texttt{luke.skywalker@uniud.it}
}
\end{verbatim}
\item[\texttt{marker}] you can use \texttt{\textbackslash marker} to highlight some text. The default color is \marker{orange}, but you can also \marker[UniBlue]{use a custom color}. For example:
\begin{verbatim}
\marker{Default color}
\marker[UniBlue]{Custom Color}
\end{verbatim}
\item[\texttt{framefill}] you can use \texttt{\textbackslash framefill} to put the text at the bottom of a slide by filling all the vertical space.
\end{description}

\end{frame}

\end{document}